DATA 605 Week 8 Assignment

### 2019-03-23 DATA605/MSilva_Assign8.Rmd
More work
Finished Assignment 8

**Assume that X1 and X2 are independent random variables, each having an exponential density with parameter λ. Show that Z = X1 − X2 has density**

$$fz(z)=(1/2)\lambda e ^{-\lambda \mid z \mid}$$

@@

@@

@@

@@

@@

>>>>

**Assume that X1 and X2 are independent random variables, each having an exponential density with parameter λ. Show that Z = X1 − X2 has density $fz(z)=\frac{1}{2}\lambda e ^{-\lambda \mid z \mid}$**

*Note: In order to keep this straigth in my head I solved Z = X - Y instead of Z = X1 - X2.  This notation will be used in this solution.*

The convolution formula of Z = X + Y is

$$fx(z) = \int_{-\infty}^{\infty}fx(x)fy(z-x)dx$$

But to do Z = X - Y we need to do Z = X + (-Y).  Pluging it into the convolution formula:

$$fz(z) = \int_{-\infty}^{\infty}fx(x)f{-y}(z-x)dx$$
Since $f{-y}(z-x) = fy(x-z)$ we can rewrite the convolution as

$$fz(z) = \int_{-\infty}^{\infty}fx(x)fy(x-z)dx$$

Looking at the case where z < 0

$$ \int_{0}^{\infty}\lambda e ^{-\lambda x} \lambda e ^ {-\lambda(x-z)}dx = \lambda e ^ {\lambda z}\int_{0}^{\infty}\lambda e ^{-2\lambda x} dx = \lambda e ^{\lambda z}(-\frac{1}{2}e ^ {-\lambda x}|_0^{\infty}) = \frac{1}{2}\lambda e^{\lambda z}$$

Now looking at the case where z is greater than or equal to zero.  Since the two variables are independent Z = X - Y is the same as -Z = -X + Y.  So the distribution is symetric arround zero thus fz(z) = fz(-z). Sp when z >= 0:

$$fz(-z) = \frac{1}{2}\lambda e^{-\lambda z}$$

This implies that $fz(z)=\frac{1}{2}\lambda e ^{-\lambda \mid z \mid}$

@@

```{r}
mu <- 10
sigma <- sqrt(100/3)
```

@@

```{r}
k <- 2 / sigma
1 / k^2
```

@@

```{r}
k <- 5 / sigma
1 / k^2
```

@@

```{r}
k <- 9 / sigma
1 / k^2
```

@@

```{r}
k <- 20 / sigma
1 / k^2
```
